---
title: "hw06"
author: "Peiyuan Zhu"
date: '2018-11-09'
output: html_document
---
```{r}
setwd("~/Desktop/hw05-garyzhubc")
suppressPackageStartupMessages(require(tidyverse))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(singer))
```
#1. Character data
Read and work the exercises in the Strings chapter or R for Data Science
##14.2.5 Exercises
###1 
paste0 is equivalent to str_c(.) and paste is equivalent to str_c(.,sep=""). paste and paste0 sees NA as string.
```{r}
paste("a","b")
paste0("a","b")
paste(NA,"b")
paste0(NA,"b")
str_c("a","b","c",sep = " ")
```
###2
Sep seperates string between vectors; collapse connects the results in one.
```{r}
paste(c("a","b","c"),c("d","e","f"),sep="/")
paste0(c("a","b","c"),c("d","e","f"),sep="/",collapse="-")
```
###3
If even then change +1 to some other number, depending on how you define "the middle number"
```{r}
str_sub("abcde",str_length("abcde")/2+1,str_length("abcde")/2+1)
```
###4
wrap string into paragraph
```{r}
cat(str_wrap("abb bbb cbb dbb",width = 10))
```
###5
Trimout the white space in the front and at the end of the string
```{r}
str_trim(" abcde ")
```
###6
```{r}
cat_str <- function(string) {
  if (length(string) == 1) {
    return(string[1])
  }
  return(paste0(string[1],cat_str(string[2:length(string)])))
} 
cat_str(c("a","b","c"))
```
##14.3.1.1
###1

###2

##14.3.2.1
###1
```{r}

```
###2
```{r}
str_view(stringr::words, "^y", match=TRUE)
str_view(stringr::words, "x$", match=TRUE)
str_view(stringr::words, "^...$", match=TRUE)
str_view(stringr::words, "^.{7,}$", match=TRUE)
```

##14.3.3.1
###1
```{r}
str_view(stringr::words, "^[aeiou]", match=TRUE)
str_view(stringr::words, "^[^aeiou]", match=TRUE)
str_view(stringr::words, "ed$|^eed$", match=TRUE)
str_view(stringr::words, "ing$|ise$", match=TRUE)
```
###2
```{r}

```
###3
```{r}
str_view(c("qu","qa"), "q[^u]", match=TRUE)
```
###4
```{r}
str_view(c("color","colour"), "ou", match=TRUE)
```
###5
```{r}
str_view(c(1604,86752), "1604", match=TRUE)
```
#14.3.4.1
###1
```{r}
"{0,1}"
"{1,}"
"{0,}"
```

###2
```{r}

```

###3
```{r}

```


##14.3.5.1
###1
```{r}

```
###2
```{r}

```


#2. Writing functions
```{r}
le_lin_fit <- function(dat, offset = 1952) {
  the_fit <- MASS::rlm(lifeExp ~ I(year - offset), dat)
  setNames(coef(the_fit), c("intercept", "slope"))
}
le_lin_fit(gapminder %>% filter(country == "Australia"))
le_lin_fit(gapminder %>% filter(country == "China"))
```
